\chapter{Introduction.}
\label{chap:introduction}


The Horus system proved that using a time series when measuring data is more efficient and accurate if it's used in an Indoor Positioning System to determine position than single values.
Providing a filter to accurately predict and remove noise from measurements is a very active research area.
It can be applied as preprocessing algorithm to a WLAN to make steady connection to an Access Point.
In some cases, these factors are very important, but are hard to find a solution to. 
Analysis of time series of wifi rssi measurements could lead to the development of an efficient client site filtering method for indoor positioning systems.
There are various time series filtering methods in the literature. This paper focuses only on two simple solution which are based on time windowing.
In the case that the two filters work efficiently, the process could be applied to networks with different filters to reach an optimal solution.
Computational complexity also gives an important constrain of these filtering methods, because the client devices usually have limited computational capacity and battery life.

\section{ILONA}
The presented results are connected to the Indoor Positioning Research at the University of Miskolc. The ILONA System is web application for indoor positioning. It provides positioning functions for client. 
The INdoor LOcation and NAvigation System is a web application, which was
created to perform indoor positioning and navigation tasks.
It is made up by loosely coupled components such as \texttt{measurement, positioning, navigation} and \texttt{tracking}.
This paper focuses on the data analysis and data mining of the ILONA System.
A proper client side filetering method could increase the performance and the accuracy of the positioning service of the ILONA System.

